Extended Abstract: Grounding Language to Reward Functions With Abstract Markov Decision Processes

### 2016-05-05 paper/paper-template-latex/paper_template.tex
Add paper update

To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands and their respective demonstrations. The following are some examples of natural language commands at each level of the AMDP:

@@

Our experiment consists of training IBM II Translation Models between every permutation of the levels of the AMDP. More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP. We then
\subsection{Results}

@@

\section{Conclusion}
\label{sec:conclusion}

\section*{Acknowledgments}

>>>>

To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands that match the given level's abstraction and their respective demonstrations. The following are some examples of natural language commands at each level of the AMDP:

@@

Our experiment consists of training IBM II Translation Models between every permutation of the levels of the AMDP. More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP. We then evaluate the models by passing in a natural language command of a given level into each of the three models. In this ``swap'', we show that we get the best results for a given level of the AMDP with the corresponding natural language command, rather than any others. We use Leave-One-Out (LOO) accuracy as the evaluation metric.

\subsection{Results}

The following table shows our LOO results for each swap. The rows are labeled with the level of the Natural Language (NLP) command, while the Columns designate the level of the MDP to which the language is grounded (the level-specific IBM II Translation system.)

\begin{table}[h!]
\centering
\caption{LOO Accuracy for each Swap}
\label{my-label}
\begin{tabular}{l|l|l|l|}
\cline{2-4}
                                  & MDP Level 0 & MDP Level 1 & MDP Level 2 \\ \hline
\multicolumn{1}{|l|}{NLP Level 0} & 0.0 \%      & 0.0\%       & 0.0\%       \\ \hline
\multicolumn{1}{|l|}{NLP Level 1} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
\multicolumn{1}{|l|}{NLP Level 2} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
\end{tabular}
\end{table}

\section{Conclusion and Future Work}
\label{sec:conclusion}

@@
